Cosmological constraints from the redshift dependence of the galaxy angular 2-point correlation function

### 2016-10-06 draft/draft1.tex
updates

\begin{abstract}
We use the redshift dependence of the galaxy angular 2-point correlation function (2pCF) shape 
to constrain cosmological parameters.
A wrongly adopted cosmology introduces redshift-dependent mis-scaling 
of the constructed galaxy distribution,
leading to redshift-dependent rescaling in the measured angular 2pCF.
We test our method on the HR4 mock galaxies having hundreds of millions of galaxies at redshifts 
0, 0.5, 1, 1.5, 2.
We find the redshift evolution of shape of angular 2pCF, as a function of scale,
is sensitive to the adopted cosmological parameters. 
It is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the redshift space distortion.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future photometric surveys like DES, LSST 
to derive tight cosmological constraints.
The work is a continue of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters based on some nearly redshift-invariant physical quantity;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

As one geometrical effect of cosmological parameters on LSS,  
when an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space,
geometric distortions are produced in the constructed galaxy distribution. 
These distortion include the ``volume effect'' which is the mis-scaling of the size of structures,
and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
%Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
%There have been a series of works studying the application of the AP test to the LSS

Various statistically methods has been proposed to measure these effects.
The AP effect has been proposed to measure through the clustering of galaxies \citep{Ballinger1996,Matsubara1996} which has been applied to a series of LSS surveys
\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
the alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed able to probe the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996} and topology \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

@@

In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from LSS data.
%proposed a series of methods to probe the geometric information encoded in the LSS data.
We found fact that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
this phenomenon can be utilized to distinguish the \scr{AP effect(?)} the from the other effects such as the redshift space distortion (RSD).
The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
It is the major systematic effects limiting our ability to probe the geometry of LSS from galaxy distribution.
We found its influence is significantly reduced in case of studying the redshift dependence of the distortion.

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing the redshift evolution of the statistical property of the gradient field 
can be used to infer unbiased constraints on certain cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the direction.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
The RSD effect, significantly distorts $\xi(\mu)$, however it
exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependent of the AP effect, 
and we come up with tight cosmological constraints comparable to the mainstream probes of SNIa, BAO, CMB and so on.

In this paper we continue our exploration of our strategy and presented 
a new method using the redshift of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to the HR4 mock galaxies having hundreds of million galaxies at redshfits 0-2
and develop the statistical procedure to constrain cosmological parameters.

@@

%Considering we are Let us consider an object in the universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
In this section we briefly introduce the scaling effect caused by wrongly assumed cosmological parameters.
A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.

Suppose that we are probing the size of some objects in the Universe.
We measure its redshift span $\Delta z$ and angular size $\Delta \theta$,
then compute its sizes in the radial and transverse directions using the following formulas
\begin{equation}\label{eq:distance}
\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\perp}=(1+z)D_A(z)\Delta \theta,
\end{equation}
where $H$ is the Hubble parameter and $D_A$ is the angular diameter distance.
In the particular case of a flat universe composed by a cold dark matter component and a constant EoS dark energy component, they take the forms of
\begin{eqnarray}\label{eq:HDA}
& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
& &D_A(z) = \frac{1}{1+z}r(z)=\frac{1}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
\end{eqnarray}
where $a=1/(1+z)$ is the cosmic scale factor,
$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.

In case wrong values of $\Omega_m$ and $w$ are adopted, 
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are wrong,
resulting in wrong estimations of the object's shape (AP effect) and size (volume effect).
These effects and their cosmological consequences have been studied in \cite{Li2014,Li2015,Li2016}.

In this paper we focus on the mis-estimation of the angular size $\Delta r_{\perp}$. %scaling of angular size,
The ratio of mis-estimation is
\begin{equation}\label{eq:DA}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \alpha_{\perp} \equiv \frac{\Delta r_{\perp, \rm wrong}}{\Delta r_{\perp, \rm true}}
 = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values in the true cosmology and wrongly assumed cosmologies, respectively.

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
as a result, 
the shapes of the squares appear distorted (AP effect),
and their sizes are wrongly estimated (volume effect).
Cosmological models (i,iii) yield to compressed size (in both angular and LOS direction),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

The mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$, 
is displayed in the right panel of Figure \ref{fig_xyquan}.
In all cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves a lot in the redshift range $0<z<2$.
As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
the angular size is underestimated by 
%12.5\%, 17.7\%, 20.1\%, 21.3\%
8.9\%, 12.3\%, 13.6\%, 14.1\% 
at $z=0.5,1,1.5,2$.

@@

In sum, as a consequence of incorrect cosmologies, 
the size of objects is mis-estimated, and the magnitude of mis-estimation depends on the redshift.
We use the galaxy angular 2pCF to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.

@@

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in unit of $ 10^{-2} h^{3} \rm Mpc^{-3}$,
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.

@@

\scr{When the correct cosmology is adopted the cosmic scale is correctly estimated,
the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
With the decreasing the redshift, we clearly see the clusters and filaments form and grow.
On the other hand, when the wrong cosmology is adopted, there is an artificial scaling of scales in the constructed map.
The separations among galaxies are over-estimated by 
$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
leading to a clear redshift evolution of sizes of structures.}

The growth of structure enhances the clustering and results in more compact structures,
while the volume effect maintains the clustering pattern and uniformly re-scales the structures on all scales.
The imprint of each of these effects on the large scale structure is different and should be distinguishable.
In the following section we show that they affect the angular correlation function measurements in different ways, 
and thus can be easily separated.

@@

Considering the large number of galaxies and random points the 2pCF is computed part by part in subsamples with 
size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
The `sheet'-like shape of the subsample is similar to the shape of redshift shells in the real observational case.
The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
and the X-Y directions %with each of width $1575 h^{-1}\ \rm Mpc$ 
are the angular plane.
For our simulation box size we have 120 such subsamples.
The average of the measurements in all subsamples is taken as the 2pCF of the whole sample,
while the covariances of them are taken to be the covariance matrix (after multiplying a factor of $1/\sqrt{119}$).

@@

Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced most growth.
$\omega(r_\perp)$ also increases with redshift at $z>1$ with increasing redshift 
as a reason of increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Apart from the large variation in amplitude between the different redshifts bins, 
%The shape of $r_\perp\omega$ also evolves with redshift.
the shape of $r_\perp\omega$  is similar at all redshifts;
in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures 
and is much more significant at lower redshift.

In order to directly compare the shape of 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\omega$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modelling of the shape of the angular 2pCF is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
instead of using our method 
(although our method should also be applicable).

In the upper-middle panel, the overlapping $\hat\omega$'s
clearly show the minimal redshift evolution of the shape.
In the upper-right panel, 
we further show the residual evolution at high redshifts 
with respect to $z=0$.
There is only 1-4\% enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

There is one detail in the analysis that should be emphasized here.
In real observations we may be selecting {\it different} types of galaxies at different redshifts.
Considering this fact in the comparison of $\hat\omega_{r_\perp}$ 
we compare subsamples of galaxies at {\it different} locations.
As an example, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
at higher redshifts we then adopt measurement within $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$ for a comparison.
%and take the difference between them to get $\delta \hat{r_\perp\omega}$.
%So we are always comparing 2pCF measured from different samples of galaxies.
If we simply compare the 2pCF of the {\it same} subsample of galaxies at different redshifts, 
one would significantly underestimate the statistical uncertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring the cosmic variance.
%The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
%\footnote{In all figures of this paper The error bars displayed in all figures are estimated in this way; 
%from the 120 subsamples and for the error bar of redshift evolution of 2pCF 
%we always take the cosmic variance into consideration.}.

@@

The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
the higher the redshift, the more the enhancement.%the amplitude monotonically increases as a function of redshift.

>>>>

\begin{abstract}
We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
for a purpose of cosmological constraints.
When an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we find a redshift-dependent rescaling in the measured galaxy angular 2pCF .
We test our method on the HR4 mock galaxies having hundreds of millions of galaxies at redshifts 
$0\leq z\leq2$.
We find the redshift evolution of shape of angular 2pCF, as a function of scale,
is sensitive to the adopted cosmological parameters,
and is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the redshift space distortion.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially the photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constraining cosmological parameters based on some nearly redshift-invariant physical quantity;
they are all powerful in constraining cosmology and have a lot of merit,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
do not require accurate analytical modeling of the galaxy correlation function,
and are applicable on relatively small clustering scales.
\end{abstract}

@@

%As one geometrical effect of cosmological parameters on LSS,  
When an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space,
geometric distortions are produced in the constructed galaxy distribution. 
These distortions include the ``volume effect'' which is the mis-scaling of the size of structures,
and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
%Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
%There have been a series of works studying the application of the AP test to the LSS

Various statistical methods have been proposed to measure these effects.
The AP effect can be measured through statistical study of the clustering of galaxies \citep{Ballinger1996,Matsubara1996}.
This method has been applied to a series of LSS surveys
\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016},
Alternative approaches uses the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed that are able to probe the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996} and topology \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

@@

In \cite{Li2014,Li2015,Li2016} we developed a novel strategy to probe $D_A$ and $H$ from LSS data.
%proposed a series of methods to probe the geometric information encoded in the LSS data.
We found that the AP or volume effect in general introduces a geometric distortion that evolves significantly with redshift;
this phenomenon can be utilized to distinguish the AP effect from the other effects, such as the redshift space distortion (RSD).
The radial distances of galaxies are inferred from the measured redshifts, which are distorted by the peculiar motion of galaxies, 
leading to apparent distortion in the redshift space galaxy distribution \citep{FOG,Kaiser1987,Ballinger1996}.
This is the major systematic effect limiting our ability to probe the geometry of LSS from galaxy distribution.
We found its influence is significantly reduced when studying the redshift dependence of the distortion.

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulation \citep{horizonrun},
showing that the redshift evolution of the gradient field 
can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the direction between the connection of the galaxy pairs and the line of sight.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
Although the RSD effect significantly distorts $\xi(\mu)$, 
it exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
and we arrive at tight cosmological constraints comparable to mainstream probes of SNIa, BAO, CMB.

In this paper we continue our exploration of this strategy and presented 
a new method using the redshift of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to HR4 mock galaxies, using hundreds of millions of galaxies at redshfits $0\leq z\leq2$
and develop the statistical procedure to constrain cosmological parameters.

@@

%Considering we are Let us consider an object in the universe with certain size and shape.
%Its observed redshift span $\Delta z$ and angular size $\Delta \theta$ are related with the comoving sizes by
In this section we briefly introduce the scaling effect caused by incorrectly assumed cosmological parameters.
A more detailed description has been provided in \cite{Li2014,Li2015,Li2016}.

Suppose that we are probing the size of some objects in the Universe.
We measure their redshift span $\Delta z$ and angular size $\Delta \theta$,
then compute their sizes in the radial and transverse directions using the following formulas
\begin{equation}\label{eq:distance}
\Delta r_{\parallel} = \frac{c}{H(z)}\Delta z,\ \ \Delta r_{\perp}=(1+z)D_A(z)\Delta \theta,
\end{equation}
where $H$ is the Hubble parameter and $D_A$ is the angular diameter distance.
In the particular case of a flat universe composed of a cold dark matter component and a constant EoS dark energy, they take the forms
\begin{eqnarray}\label{eq:HDA}
& &H(z) = H_0\sqrt{\Omega_ma^{-3}+(1-\Omega_m)a^{-3(1+w)}},\nonumber\\
& &D_A(z) = \frac{1}{1+z}r(z)=\frac{1}{1+z}\int_0^z \frac{dz^\prime}{H(z^\prime)},
\end{eqnarray}
where $a=1/(1+z)$ is the cosmic scale factor,
$H_0$ is the present value of Hubble parameter and $r(z)$ is the comoving distance.

When incorrect values of $\Omega_m$ and $w$ are adopted, 
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are also wrong,
resulting in wrong estimations of the object's shape (AP effect) and size (volume effect).
These effects and their cosmological consequences have been studied in \cite{Li2014,Li2015,Li2016}.

In this paper we focus on the mis-estimation of the angular size $\Delta r_{\perp}$. %scaling of angular size,
The ratio of mis-estimation is
\begin{equation}\label{eq:DA}
 %{\rm Degree\ of\ volume\ magnification \equiv}
 %{\rm rat}_{\rm volume\ mag}\equiv
 \alpha_{\perp} \equiv \frac{\Delta r_{\perp, \rm wrong}}{\Delta r_{\perp, \rm true}}
 = \frac{D_{A, \rm wrong}}{D_{A, \rm true}},
\end{equation}
where ``true'' and ``wrong'' denote the values in the true cosmology and wrongly assumed cosmologies respectively.

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
then the shapes of the squares appear distorted (AP effect),
and their sizes are wrongly estimated (volume effect).
Cosmological models (i,iii) yield to compressed size (in both angular and LOS direction),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

The mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$, 
is displayed in the right panel of Figure \ref{fig_xyquan}.
In all cosmologies, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$ evolves significantly in the redshift range $0\leq z\leq 2$.
As an example, when adopting the quintessence cosmology $\Omega_m=0.26,\ w=-0.5$,
the angular size is underestimated by 
%12.5\%, 17.7\%, 20.1\%, 21.3\%
8.9\%, 12.3\%, 13.6\%, 14.1\% 
at $z=0.5,1,1.5,2$.

@@

In sum, as a consequence of incorrect cosmologies 
the size of objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
We use the galaxy angular 2pCF to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.

@@

%As will be introduced in the next section, 
%The output of HR4 simulation includes one all-sky light cone mock galaxy catalogue reaching $r=3\,150$ ${h^{-1}}$Mpc 
%and a series ({\bf how many?}) of snapshot mock galaxy catalogues at different redshifts.
We take the snapshot data of the mock galaxies at $z=0,0.5,1,1.5,2$.
%We require subhalos to have at least 30 member particles, 
%so the minimal mass of galaxies is $\simeq m_{p} \simeq 2.7 \times 10^{11} \hMsun$.
Setting a minimal halo mass of $3\times 10^{11} \hMsun$, 
%$4.57\times 10^8$, $4.06\times 10^8$, $3.52\times 10^8$, $3.06\times 10^8$ and $2.28 \times 10^8$ mock galaxies,
we select 457, 406, 352, 206 and 228 million mock galaxies at the five redshifts,
corresponding to a number density of 
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
1.46, 1.30, 1.13, 0.98 and 0.73 in units of $ 10^{-2} h^{3} \rm Mpc^{-3}$
%$1.46\times 10^{-2}$, $1.30\times 10^{-2}$, $1.13\times 10^{-2}$, $0.98\times 10^{-2}$ and $0.73\times 10^{-2}\ (h^{-1} \rm Mpc)^{-3}$,
respectively.
Applying a uniform mass cut, at higher redshift we obtained a smaller number of galaxies with {\it larger bias}.

@@

\scr{When the correct cosmology is adopted the cosmic scale is correctly estimated,
the main factor leads to redshift evolution of galaxy distribution is the gravitational growth of structure.
With decreasing redshift, we clearly see the clusters and filaments form and grow.
On the other hand, when the wrong cosmology is adopted, there is an artificial scaling of distances in the constructed map.
The separations among galaxies are over-estimated by 
$25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$,
leading to a clear redshift evolution of sizes of structures.}

The growth of structure increases the clustering and results in more compact structures,
while the volume effect maintains the clustering pattern and uniformly re-scales structures on all scales.
The imprint of each of these effects on the large scale structure is different and should be distinguishable.
In the following section we show that they affect the angular correlation function measurements in different ways, 
and thus can be easily separated.

@@

Considering the large number of galaxies and random points the 2pCF is computed part by part in subsamples with 
size of 1575 $h^{-1}{\rm Mpc}\times 1575\ h^{-1}{\rm Mpc}\times 105\ h^{-1}{\rm Mpc}$.
The `sheet'-like shape of the subsample is similar to the shape of redshift shells in the real observational case.
The Z direction with thickness $105\ h^{-1}\rm Mpc$ is treated as the radial direction (the $r$ direction) 
and the X-Y directions %with each of width $1575 h^{-1}\ \rm Mpc$ 
are the angular plane.
For our simulation box size we have 120 such subsamples.
The average of the measurements in all subsamples is taken as the 2pCF of the whole sample,
while the covariances of them are taken to be the covariance matrix (after multiplying by a factor of $1/\sqrt{119}$).

@@

Among different redshifts there is large variation in the amplitude of $\omega(r_\perp)$.
The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced the most growth.
$\omega(r_\perp)$ also increases with redshift at $z>1$ with increasing redshift 
as a reason of increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Although there is large variation in amplitude between the different redshifts bins, 
%The shape of $r_\perp\omega$ also evolves with redshift.
the shape of $r_\perp\omega$  remains similar at all redshifts;
in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures 
and is much more significant at lower redshift.

In order to directly compare the shape of the 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\omega$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modelling of the shape of the angular 2pCF is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{Salvador2014,Salvador2016} 
instead of using our method 
(although our method should also be applicable).

In the upper-middle panel, the overlapping of $\hat\omega$
clearly show the minimal redshift evolution of the shape.
In the upper-right panel, 
we further show the residual evolution at high redshifts 
with respect to $z=0$.
There is only 1-4\% enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

There is one detail in the analysis that should be emphasized here.
In real observations we may be selecting {\it different} types of galaxies at different redshifts.
Considering this fact in the comparison of $\hat\omega_{r_\perp}$ 
we compare subsamples of galaxies at {\it different} locations.
As an example, if at $z=0$ we take $\hat\omega_{r_\perp}$ measured within $0h^{-1}{\rm Mpc}<Z<105 h^{-1}{\rm Mpc}$,
at higher redshifts we then adopt measurement within $105h^{-1}{\rm Mpc}<Z<210 h^{-1}{\rm Mpc}$ for a comparison.
%and take the difference between them to get $\delta \hat{r_\perp\omega}$.
%So we are always comparing 2pCF measured from different samples of galaxies.
If we simply compare the 2pCF of the {\it same} subsample of galaxies at different redshifts, 
one would significantly underestimate the statistical uncertainty of $\delta \hat{\omega}_{r_\perp}$ by ignoring cosmic variance.
%The error bars and covariance are always estimated in this way to take the cosmic variance into consideration.
%\footnote{In all figures of this paper The error bars displayed in all figures are estimated in this way; 
%from the 120 subsamples and for the error bar of redshift evolution of 2pCF 
%we always take the cosmic variance into consideration.}.

@@

The mis-scaling not only changes the shape of the 2pCF but also modifies its amplitude. %The amplitude of $r_\perp\omega$ is amplified due to the stretch of scale.
As is shown in the left panel, due to the stretch of scale the amplitude is enhanced at higher redshifts;
the higher the redshift, the greater the enhancement.%the amplitude monotonically increases as a function of redshift.
